Associative Data Structures for Website Filtering

### 2014-04-17 paper/paper.tex
Results section

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{hyperref}

@@

    Our results were great!  They are best analysed with a two-sample independent T test.  We had an
    equal number of measurements about group 1 (with mean $x_1$ and standard deviation $\sigma_1$ and
    about group 2 (with mean $x_2$ and standard deviation $\sigma_2$).  From this we can conclude that
    data structure 1 is, on average, unquestionably superior.

@@

    \section{Conclusions}
    Our main point of research was researching which associative data structure performed best on a
    various number of insertions, in terms of the speed of insertions and look-ups, and memory
    usage.  In terms of speed we can state with certainty that the hash table is the superior data
    structure.  It outperforms the other two in almost every category, most significantly in larger
    datastructures where it often takes less than half as much time as the skiplist and less than
    two thirds the time of the binary search tree.  In most cases, the binary search tree is a bit
    slower, whereas the skip list is the slowest structure in virtually every case. The only
    motivation for using a hashmap for this problem appears to be in memory usage, although the
    advantage gained from this is relatively small.

@@

>>>>

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{hyperref}
\usepackage[pdftex]{graphicx}

@@

    Now that we have done the tests we have gained a lot of data that we can analyze and base our 
    conclusions on. To do this, we will need to make our data more easily readable and use statistical
    tests to draw conclusions.

     First, to get an overview of our data, we will determine the averages for each scenario
    (Datastructure, keytype and number of entries). For these averages we will look at operation speed per
    element and memory usage per element. These can be seen in appendix \ref{App:AveResults}.

    Now we may notice patterns in these averages, but to actually draw conclusions from the results, we will
    need to use statistical methods. Depending on what results we want to compare there are different statistical
    tests we can use. For our results we shall make use of independent samples T test and bivariate correlation test.

    We shall use a significance of $0.95$ and we perform all statistical tests using the SPSS software package.

    \subsection{Correlation between number of entries and results}
    First we look at the influence the number of entries has on the per element speed of operations. For this
    we will use a bivariate correlation test, since we want to check if there exists a correlation between 
    the number of entries and the speed of operations.

    Using analysis in SPSS it turns out that for almost all situations there exists positive correlations between the number
    of entries and the speed of both queries and inserts. For both skiplist and BST these correlations are significant for all
    keytypes. In all cases they have positive correlations between $0.4$ and $0.6$.

    However in the case of hashmaps we don't always have correlations. For all situations there does exist a positive correlation
    between the number of entries and the per element query time. But for inserts there only exists a correlation when we 
    look at Ip-address keys. If we look at Domain or Full path keys, there is no significant correlation between the number of entries
    and the per element speed of insert operation.

    \subsection{Difference in performance between different keytypes}
    Another part of our research question was: ``How does the complexity of the key influence the performance of 
    various associative data structures?". Thus we would like to compare performance between the different keytypes. 
    To look at this, we will set our number of entries to 4096 and compare the different key types.

    It turns out the results are largely the same for the different data structures. For all of the data structures the use of
    Ip-addresses is significantly faster in both query and insert speeds and has lower memory usage as well, this is even true
    no matter the number of entries.

    For the difference between full path and domain the results become more complex. Looking at BST we get the following results:
    Insert speed on full paths is significantly faster than insert speed on domains, however query speed on domains is significantly faster
    than query speed on full paths.

    Looking at skiplist we get the following results: Insert speed on full paths is significantly faster than insert speed on domains. Query
    speed however does not significantly differ between domains and full paths. If we look at higher number of entries query speed becomes 
    significantly faster for full paths.

    Finally for our results with hashmap: Domains are significantly faster in both insert and query speed compared to full paths. 
    This is true no matter the number of entries.

    \subsection{Comparison between different data structures}
    We would like to be able to use our results to determine which data structures are better in which cases. 
    For this we will have to compare the different data structures for specific situations. We will use an independent
    samples T test for this, since our data points are independent of each other.

    First off, for almost all situations with the keytypes Full path and Domain, hashmap is significantly faster than BST and skiplist
    in both query speed and in insert speed. The only exception is in the case of 256 entries, which is most likely a
    problem in our setup.

    More interesting are the speeds in the case of the Ip-addresses. While the hashmap is still significantly faster 
    for query speeds, no matter the number of entries, there is a different result for the insert speeds. For 4096
    entries or less, the BST significantly outperforms the hashmap in terms of insert speed. For any number of 
    entries higher than that, the hashmap outperforms the BST again.

@@

    \section{Conclusions}
    Our main point of research was researching which associative data structure performed best on a
    various number of insertions, in terms of the speed of insertions and look-ups, and memory
    usage.  In terms of speed we can state with certainty that the hash table is the superior data
    structure.  It outperforms the other two in almost every category, most significantly in larger
    datastructures where it often takes less than half as much time as the skiplist and less than
    two thirds the time of the binary search tree.  In most cases, the binary search tree is a bit
    slower, whereas the skip list is the slowest structure in virtually every case. The only
    motivation for using a skiplist for this problem appears to be in memory usage, although the
    advantage gained from this is relatively small.

@@

    \newpage
    \appendix
    \section{Average results} \label{App:AveResults}

    \begin{figure}[h!]
    \centering
    \includegraphics[width=\textwidth]{Ip-address_averages.png}
    \caption{The average per element results for each situation with Ip-adresses.}
    \end{figure}

    \begin{figure}[h!]
    \centering
    \includegraphics[width=\textwidth]{Domain_averages.png}
    \caption{The average per element results for each situation with domain adresses.}
    \end{figure}

    \begin{figure}[h!]
    \centering
    \includegraphics[width=\textwidth]{Full_path_averages.png}
    \caption{The average per element results for each situation with full path adresses.}
    \end{figure}
